\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-06-25 ms.tex
cite naomi

% TODO: before submission

% TODO: after submission?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
% - Is the cluster elongated along its orbit?
% - Describe the strength of the hierarchical cluster params methodology
% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
% - https://ui.adsabs.harvard.edu/#abs/2008ApJ...673L.143M/abstract

@@

The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the MS gas in this region has passed through the Galactic midplane.
The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the MS, but were decelerated through interactions with Milky Way gas?
This presents a possible formation scenario for \clustername.
If the cluster formed from the LA gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.
Given the geometry of the current location of \clustername\ (i.e. our viewing angle from the solar position), in this scenario we would expect a moderate velocity difference between the gas that interacted and stars to primarily appear as a difference in the tangential velocities of the stars and the gas (which is not measured).
We can therefore use the line-of-sight velocity of the gas as a proxy for the line-of-sight velocity of the stars in \clustername\ to study the Galactic orbit of the cluster, as discussed in the next section, and because we do not yet have radial velocity information for the stars.

>>>>

% TODO: after submission?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
% - Describe the strength of the hierarchical cluster params methodology
% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.

@@

The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the MS gas in this region has passed through the Galactic midplane.
The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the MS, but were decelerated through interactions with Milky Way gas?
\changestwo{This scenario has been suggested (i.e., that the LA material has interacted with gas in the Galactic disk) based on the kinematics and morphology of a LA HVC \citep{McClure-Griffiths:2008}} and presents a possible formation scenario for \clustername.
If the cluster formed from the LA gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.
Given the geometry of the current location of \clustername\ (i.e. our viewing angle from the solar position), in this scenario we would expect a moderate velocity difference between the gas that interacted and stars to primarily appear as a difference in the tangential velocities of the stars and the gas (which is not measured).
We can therefore use the line-of-sight velocity of the gas as a proxy for the line-of-sight velocity of the stars in \clustername\ to study the Galactic orbit of the cluster, as discussed in the next section, and because we do not yet have radial velocity information for the stars.
